MATLAB: Read Me

### 2020-04-19 LaTeX_Code/Paper/paper_1line.tex
Added from section 4.3 to section 7 in the paper. Added optimization for the other two datasets. Added likelihood with three parameters.

%---BEGIN SECTION 6---
\section{Forecast Provider Comparison} \label{Section_6}
We compare forecasts from two different companies for the same period.
\begin{table}[H]
\centering
\begin{tabular}{cccc}
\toprule
Forecast Provider & parameters $(\theta_0, \alpha,\delta)$ & AIC & BIC \\ \midrule
Provider A  &  $(\add,\add)$      &  \add   & \add    \\
Provider B  & $(\add,\add) $  &  \add   &   \add  \\ 
\bottomrule
\end{tabular}
\caption{\add}
\label{tab:forcast_comparison}
\end{table}
In Figure (\add)-(\add), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.

 \begin{table}[H]
 \centering
 \begin{tabular}{cccc}
 \toprule
 Model & parameters $(\theta_0, \alpha)$  \\
 \midrule
 \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}               &  $(\add,\add) \pm (\add,\add)$   \\ 
 \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &  $(\add,\add) \pm (\add,\add)$      \\ \bottomrule
 \end{tabular}
 \caption{ \add confidence interval obtained using bootstrap}
 \label{tab:freq_comparison}
 \end{table}
%---END SECTION 6---

>>>>

%---BEGIN SECTION 6---
\section{Forecast Provider Comparison} \label{Section_6}
We compare forecasts from two different companies for the same period.
\begin{table}[H]
\centering
\begin{tabular}{ccc}
\toprule
Forecast Provider & Parameters $(\theta_0, \alpha)$ & Product $\theta_0\alpha$ \\ \midrule
Provider A  &  $(1.180,0.070)$      &  0.083    \\
Provider B  & $(0.766,0.117) $  &  0.090 \\ 
Provider C  & $(1.347,0.073) $  &  0.099 \\ 
\bottomrule
\end{tabular}
\caption{\add}
\label{tab:forcast_comparison}
\end{table}

%---END SECTION 6---

### 2020-04-19 LaTeX_Code/Paper/paper_1line_Renzo.tex
Added from section 4.3 to section 7 in the paper. Added optimization for the other two datasets. Added likelihood with three parameters.

%---BEGIN SECTION 6---
\section{Forecast Provider Comparison} \label{Section_6}
We compare forecasts from two different companies for the same period.
\begin{table}[H]
\centering
\begin{tabular}{ccc}
\toprule
Forecast Provider & Parameters $(\theta_0, \alpha,\delta)$ & Product $\theta_0\alpha$ \\ \midrule
Provider A  &  $(\add,\add)$      &  \add    \\
Provider B  & $(\add,\add) $  &  \add \\ 
Provider C  & $(\add,\add) $  &  \add \\ 
\bottomrule
\end{tabular}
\caption{\add}
\label{tab:forcast_comparison}
\end{table}
In Figure (\add)-(\add), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.

>>>>

%---BEGIN SECTION 6---
\section{Forecast Provider Comparison} \label{Section_6}
We compare forecasts from two different companies for the same period.
\begin{table}[H]
\centering
\begin{tabular}{ccc}
\toprule
Forecast Provider & Parameters $(\theta_0, \alpha)$ & Product $\theta_0\alpha$ \\ \midrule
Provider A  &  $(1.180,0.070)$      &  0.083    \\
Provider B  & $(0.766,0.117) $  &  0.090 \\ 
Provider C  & $(1.347,0.073) $  &  0.099 \\ 
\bottomrule
\end{tabular}
\caption{\add}
\label{tab:forcast_comparison}
\end{table}

### 2020-04-19 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
Added some references.
Added from section 4.3 to section 7 in the paper. Added optimization for the other two datasets. Added likelihood with three parameters.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{../Results/likelihood/normal/Log-Likelihood.eps}
%\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_refined.eps}
%\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_more_refined.eps}
\caption{We use the code \textbf{plotLogLikelihood.m} to create this plots. We used about 18 thousand transitions, and we can also see the initial guess.}
\end{figure}

@@

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{../Results/likelihood/normal/Log-Likelihood.jpg}
%\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_refined.eps}
%\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_more_refined.eps}
\caption{We use the code \textbf{plotLogLikelihood.m} to create this plots. We used about 18 thousand transitions, and we can also see the initial guess.}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../Results/likelihood/normal/Log-Likelihood_Zoom.eps}
\includegraphics[width=0.41\textwidth]{../Results/likelihood/lamperti/Log-Likelihood_Zoom.eps}
\end{figure}
